---
title: "MSDS 6306 - Case Study 2 Project"
author: "Swee Chew, Mallory Hightower, Shon Mohsin and Laura Niederlander"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

data import and tidy data

```{r}
url <- "http://archive.ics.uci.edu/ml/machine-learning-databases/communities/communities.data"
unstcrimedata <- read.csv(url, header = FALSE)
dim(unstcrimedata)
# head(unstcrimedata)
colnames(unstcrimedata) <- c("state", "county", "community", "communityname", "fold", "population", "householdsize", "racepctblack", "racePctWhite", "racePctAsian", "racePctHisp", "agePct12t21", "agePct12t29", "agePct16t24", "agePct65up", "numbUrban", "pctUrban", "medIncome", "pctWWage", "pctWFarmSelf", "pctWInvInc", "pctWSocSec", "pctWPubAsst", "pctWRetire", "medFamInc", "perCapInc", "whitePerCap", "blackPerCap", "indianPerCap", "AsianPerCap", "OtherPerCap", "HispPerCap", "NumUnderPov", "PctPopUnderPov", "PctLess9thGrade", "PctNotHSGrad", "PctBSorMore", "PctUnemployed", "PctEmploy", "PctEmplManu", "PctEmplProfServ", "PctOccupManu", "PctOccupMgmtProf", "MalePctDivorce", "MalePctNevMarr", "FemalePctDiv", "TotalPctDiv", "PersPerFam", "PctFam2Par", "PctKids2Par", "PctYoungKids2Par", "PctTeen2Par", "PctWorkMomYoungKids", "PctWorkMom", "NumIlleg", "PctIlleg", "NumImmig", "PctImmigRecent", "PctImmigRec5", "PctImmigRec8", "PctImmigRec10", "PctRecentImmig", "PctRecImmig5", "PctRecImmig8", "PctRecImmig10", "PctSpeakEnglOnly", "PctNotSpeakEnglWell", "PctLargHouseFam", "PctLargHouseOccup", "PersPerOccupHous", "PersPerOwnOccHous", "PersPerRentOccHous", "PctPersOwnOccup", "PctPersDenseHous", "PctHousLess3BR", "MedNumBR", "HousVacant", "PctHousOccup", "PctHousOwnOcc", "PctVacantBoarded", "PctVacMore6Mos", "MedYrHousBuilt", "PctHousNoPhone", "PctWOFullPlumb", "OwnOccLowQuart", "OwnOccMedVal", "OwnOccHiQuart", "RentLowQ", "RentMedian", "RentHighQ", "MedRent", "MedRentPctHousInc", "MedOwnCostPctInc", "MedOwnCostPctIncNoMtg", "NumInShelters", "NumStreet", "PctForeignBorn", "PctBornSameState", "PctSameHouse85", "PctSameCity85", "PctSameState85", "LemasSwornFT", "LemasSwFTPerPop", "LemasSwFTFieldOps", "LemasSwFTFieldPerPop", "LemasTotalReq", "LemasTotReqPerPop", "PolicReqPerOffic", "PolicPerPop", "RacialMatchCommPol", "PctPolicWhite", "PctPolicBlack", "PctPolicHisp", "PctPolicAsian", "PctPolicMinor", "OfficAssgnDrugUnits", "NumKindsDrugsSeiz", "PolicAveOTWorked", "LandArea", "PopDens", "PctUsePubTrans", "PolicCars", "PolicOperBudg", "LemasPctPolicOnPatr", "LemasGangUnitDeploy", "LemasPctOfficDrugUn", "PolicBudgPerPop", "ViolentCrimesPerPop")
crimedata <- unstcrimedata
summary(crimedata)
head(crimedata)
```

## Data Set Citations
U. S. Department of Commerce, Bureau of the Census, Census Of Population And Housing 
1990 United States: Summary Tape File 1a & 3a (Computer Files),

U.S. Department Of Commerce, Bureau Of The Census Producer, Washington, DC and 
Inter-university Consortium for Political and Social Research Ann Arbor, Michigan. 
(1992)

U.S. Department of Justice, Bureau of Justice Statistics, Law Enforcement Management 
And Administrative Statistics (Computer File) U.S. Department Of Commerce, Bureau Of 
The Census Producer, Washington, DC and Inter-university Consortium for Political and 
Social Research Ann Arbor, Michigan. (1992)

U.S. Department of Justice, Federal Bureau of Investigation, Crime in the United 
States (Computer File) (1995)

Redmond, M. A. and A. Baveja: A Data-Driven Software Tool for Enabling Cooperative 
Information Sharing Among Police Departments. European Journal of Operational Research 
141 (2002) 660-678. 

## Introduction

```{r}

```


## Data

```{r}

```


## Conclusion


